SKIN LESION CLASSIFICATION ON IMBALANCED DATA USING DEEP LEARNING WITH SOFT ATTENTION

### 2022-08-25 MDPI/Sensor Paper/template.tex
Update

\address{
$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, Vietnam\\
$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam}

@@

Besides the comparison between original weight loss based model and the new weight loss based model is also conducted on the three best performance model including InceptionResNetV2, DenseNet201, MobileNetV3. After the experiment, it is found out that the new weight loss function dose not only contribute to the model to overcome the data imbalance problem but it also make the accuracy increase. The performance of models is described in the Table \ref{table:loss-comparision}

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c | c |}
		\hline
		Model & Original Loss Accuracy & New Loss Accuracy\\
		\hline
		InceptionResNetV2 & 0.74 & 0.90\\
		DenseNet201 & 0.81 & 0.89\\
		MobileNetV3 & 0.80 & 0.86\\
		\hline
	\end{tabular}
	\caption{Loss based model accuracy comparison}
	\label{table:loss-comparision}
\end{table}

>>>>

\address{
$^{1}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam; dung.nguyenviet1@hust.edu.vn\\
$^{2}$ \quad Faculty of Information Technology, University of Transport and Communications, Vietnam; dnbui@utc.edu.vn\\
$^{3}$ \quad School of Electrical and Electronic Engineering, Hanoi university of Science and Technology, Vietnam; khoi.dh200322@sis.hust.edu.vn}

@@

Besides the comparison between original weight loss calculated by the sample percentage of each class model and the new weight loss based model is also conducted on the three best performance model including InceptionResNetV2, DenseNet201, MobileNetV3. After the experiment, it is found out that the new weight loss function dose not only contribute to the model to overcome the data imbalance problem but it also make the accuracy increase. The performance of models is described in the Table \ref{table:loss-comparision}

\begin{table}[H]
	\centering
	\begin{tabular}{| l | c | c | c |}
		\hline
		Model & No Weight & Original Loss Accuracy & New Loss Accuracy\\
		\hline
		InceptionResNetV2 & 0.74 & 0.79 & 0.90\\
		DenseNet201 & 0.81 & 0.84 & 0.89\\
		MobileNetV3 & 0.79 & 0.80 & 0.86\\
		\hline
	\end{tabular}
	\caption{Loss based model accuracy comparison}
	\label{table:loss-comparision}
\end{table}
